Visual Question Answering with DeepProbLog

### 2022-03-11 paper/paper.tex
Start writing for approach
Write about the generation of data

\section{LITERATURE SURVEY}
The application focuses on Visual Question Answering (VQA), for which huge datasets are present, along with very sophisticated methods. The best known dataset for VQA is CLEVR \cite{clevr_dataset}, which contains 100k images with one million questions. An example image is given in Figure \ref{fig:sample_image_clevr}, while example questions are:
\begin{itemize}
    \item Are there an equal number of large things and metal spheres?
    \item What size is the cylinder that is left of the brown metal thing that is left of the big sphere?
    \item How many objects are either small cylinders or metal things?
\end{itemize}

@@

>>>>

\section{LITERATURE SURVEY}
\label{sec:literature_survey}
The application focuses on Visual Question Answering (VQA), for which huge datasets are present, along with very sophisticated methods. The best known dataset for VQA is CLEVR \cite{clevr_dataset}, which contains 100k images with one million questions. An example image is given in Figure \ref{fig:sample_image_clevr}, while example questions are:
\begin{itemize}
    \item Are there an equal number of large things and metal spheres?
    \item What size is the cylinder that is left of the brown metal thing that is left of the big sphere?
    \item How many objects are either small cylinders or metal things?
\end{itemize}

@@

\section{APPROACH}
The implementation process involved three main parts:
\begin{enumerate}
    \item Generation of data.
    \item Creation of the logical part with DeepProbLog statements.
    \item Linking the data and controlling the training process in pure Python code.
\end{enumerate}

% TODO maybe elaborate why I switched from having a CNN per square in the grid, to one CNN per color.

\subsection{Generation of data}
As mentioned in Section \ref{sec:literature_survey}, the data used in this application is based on the Sort Of CLEVR dataset, with one extra simplification. Given that the logical part will have to decide whether an object is located on the left side of an image, the neural network will have to convey positional information to the logical part. Hence, each discrete position will have to be encoded by a possible outcome of the neural network. Therefore, objects may only be located at certain places in a grid. In this application, a grid of 2x2, 4x4 and 6x6 has been used.

The data generator that was used for the creation of the Sort Of CLEVR dataset has been modified in order to place objects in the mentioned grid positions \cite{sort_of_clevr_dataset}. An example of a generated image is given in Figure \ref{fig:sample_image_own_dataset}.

\begin{figure}[H]
    \begin{center}
    %\includegraphics[width=0.3\textwidth]{sample_own_dataset.png} TODO
    \captionsetup{justification=centering}
    \caption{A sample image from the dataset that has been used for this application}
    \label{fig:sample_image_own_dataset}
    \end{center}
\end{figure}

Each specified color will have an object located somewhere in the grid, of which the shape can be a rectangle or a circle.

These images are accompanied with three non-binary questions and one binary question. For each question, a random object is chosen. The possibilities are:
\begin{enumerate}
    \item Non-binary - What is the shape of this object \footnote{I.e. the shape will be either a rectangle or a circle.}?
    \item Non-binary - Is this object located on the left side of the image?
    \item Non-binary - Is this object located on the bottom side of the image?
    \item Binary - How many objects have the same shape of this object?
\end{enumerate}

These questions are encoded in a one-hot encoding, after which they are stored in a CSV file, along with the expected answers. A training set, a validation set, and a test set are generated. % Validation set useful?

\subsection{Logical rule encodings}

\subsection{Controlling the training process}

\section{EXPERIMENTS}
